### 2017-01-06 doc/manuscript.Rmd
Forgot to add monthsfrombaseline to manuscript
Created and added PLS fig (using HOMA2)

```{r analyze_gee, cache=TRUE}
gee_unadj_df <- analyze_gee(covars = "VN")
gee_adj_df <- analyze_gee()
```

```{r analyze_others}
# CV results are shown in pls.Rmd vignette
pls_homa <- analyze_pls(y = 'linvHOMA', cv = FALSE)
pls_isi <- analyze_pls(y = 'lISI', cv = FALSE)

# Correlation between predicted and actual
pls_homa_t <- analyze_pls(y = 'linvHOMA')
pls_isi_t <- analyze_pls(y = 'lISI')
pls_igi_t <- analyze_pls(y = 'lIGIIR')
pls_issi2_t <- analyze_pls(y = 'lISSI2')

@@

tagfa <- calc_tagfa_percent()
outcome_chg <- calc_outcome_changes()
female <- calc_discr_npct(ds0yr$Sex, 'Female')
euro <- calc_discr_npct(ds0yr$Ethnicity, 'European')
fhd <- calc_discr_npct(ds0yr$FamHistDiab, 'Yes')
est0 <- calc_gee_estci(gee_unadj_df)
est1 <- calc_gee_estci(gee_adj_df)
fa_cor <- calc_cor()
cor_pls_homa <- calc_pred_corr(pls_homa_t, pls_homa_t$test_data)
cor_pls_isi <- calc_pred_corr(pls_isi_t, pls_isi_t$test_data)
cor_pls_igiir <- calc_pred_corr(pls_igiir_t, pls_igiir_t$test_data)
cor_pls_issi2 <- calc_pred_corr(pls_issi2_t, pls_issi2_t$test_data)
```

@@

The PLS results for the insulin sensitivity (`r fig_pls`) revealed a clustering 
of the FA 14:0, 14:1n-7, 16:0, and 16:1n-7. These TAGFA loaded strongly (meaning
the FA fell between the dashed and solid circles) and negatively on 1/HOMA-IR
and ISI, suggesting this cluster of TAGFA tracks together with lower insulin
sensitivity. The TAGFA 20:2n-6, 20:5n-3, 22:5n-3, and 22:6n-3 loaded positively
on both insulin sensitivity measures. No other TAGFA loaded strongly, the
results of which remained after running the PLS model on the cross-validated
testing set. The predictive ability of the PLS model, determined by correlating
the predicted outcome values with the actual values, were good (1/HOMA-IR: 
`r cor_pls_homa$r_p`; ISI: `r cor_pls_isi$r_p`).

@@

```{r fig_pls}
gridExtra::grid.arrange(
    plot_pls(pls_homa) + ggplot2::ggtitle('A: 1/HOMA-IR'), 
    plot_pls(pls_isi) + ggplot2::ggtitle('B: ISI'), 
    ncol = 2)
```

>>>>

```{r analyze_gee, cache=TRUE}
gee_unadj_df <- analyze_gee(covars = "MonthsFromBaseline")
gee_adj_df <- analyze_gee()
```

```{r analyze_others}
# CV results are shown in pls.Rmd vignette
pls_homa2 <- analyze_pls(y = 'lHOMA2_S', cv = FALSE)
pls_isi <- analyze_pls(y = 'lISI', cv = FALSE)

# Correlation between predicted and actual
pls_homa2_t <- analyze_pls(y = 'lHOMA2_S')
pls_isi_t <- analyze_pls(y = 'lISI')
pls_igi_t <- analyze_pls(y = 'lIGIIR')
pls_issi2_t <- analyze_pls(y = 'lISSI2')

@@

tagfa <- calc_tagfa_percent()
outcome_chg <- calc_outcome_changes()
female <- calc_discr_npct(ds0yr$Sex, 'Female')
euro <- calc_discr_npct(ds0yr$Ethnicity, 'European')
fhd <- calc_discr_npct(ds0yr$FamHistDiab, 'Yes')
est0 <- calc_gee_estci(gee_unadj_df)
est1 <- calc_gee_estci(gee_adj_df)
fa_cor <- calc_cor()
cor_pls_homa2 <- calc_pred_corr(pls_homa2_t, pls_homa2_t$test_data)
cor_pls_isi <- calc_pred_corr(pls_isi_t, pls_isi_t$test_data)
cor_pls_igiir <- calc_pred_corr(pls_igiir_t, pls_igiir_t$test_data)
cor_pls_issi2 <- calc_pred_corr(pls_issi2_t, pls_issi2_t$test_data)
```

@@

The PLS results for the insulin sensitivity (`r fig_pls`) revealed a clustering 
of the FA 14:0, 14:1n-7, 16:0, and 16:1n-7. These TAGFA loaded strongly (meaning
the FA fell between the dashed and solid circles) and negatively on 1/HOMA-IR
and ISI, suggesting this cluster of TAGFA tracks together with lower insulin
sensitivity. The TAGFA 20:2n-6, 20:5n-3, 22:5n-3, and 22:6n-3 loaded positively
on both insulin sensitivity measures. No other TAGFA loaded strongly, the
results of which remained after running the PLS model on the cross-validated
testing set. The predictive ability of the PLS model, determined by correlating
the predicted outcome values with the actual values, were good (1/HOMA-IR: 
`r cor_pls_homa2$r_p`; ISI: `r cor_pls_isi$r_p`).

@@

```{r fig_pls}
gridExtra::grid.arrange(
    plot_pls(pls_homa2) + ggplot2::ggtitle('A: HOMA2-%S'), 
    plot_pls(pls_isi) + ggplot2::ggtitle('B: ISI'), 
    ncol = 2)
```
